Lyman-$\alpha$ photons through rotating outflows

### 2018-03-29 paper/paper.tex
edit

\begin{abstract}
Outflows and rotation are two ubiquitous kinematic features in the gas
kinematics of galaxies.
Here we perform Monte Carlo radiative transfer simulations of outflowing
gas with additional solid body rotation to understand how these kinematic
features impact the morphology of the Lyman-$\alpha$ emission line.
We find three important consequences of rotation.
First, it increases the detected flux at the line's center in comparison with the
non-rotational case, second it produces a line broadening and third it introduces
a dependency with the  viewing angle.
We also develp a semi-analytic model that modifies the spectra of
pure outflow simulations that manages to reproduce the main features of the
Monte Carlo simulations.
As an application to observational data we constraint the rotation
parameters of a set of observed LAE emission spectra.    
\end{abstract}

@@

Figure \ref{fig:standard_deviation} summarizes the results for STD.
Each panel shows the STD as a function of \vrot.
The black triangles correspond to the full RT solution and the line to
the Doppler Shift approximation. 
The optical depth increases from top to bottom and the outflow
velocity from left to right.
This quantitative plot confirms that the line width increases with
rotational velocity, all else being equal.
The Doppler Shift sucessfuly reproduces this trend, albeit a consistent
underestimation of the RT values; this underestimation has as an upper
bound of $\sim 7\%$, $3\%$ and $\sim 2\%$ for $\tauh=10^5$, $10^6$ and
$10^7$, respectively.
Tee Doppler Shift approximation also improves as the outflow velocity
decreases.

>>>>

\begin{abstract}
Outflows and rotation are two ubiquitous kinematic features in the gas
kinematics of galaxies.
Here we perform Monte Carlo radiative transfer simulations of outflowing
gas with additional solid body rotation to understand how these kinematic
features impact the morphology of the Lyman-$\alpha$ emission line.
We explore a range of Hydrogen optical depth of
$10^5\leq\tauh\leq10^7$, rotational velocity $0\leq \vrot/\kms \leq 100$ and
outflow velocity $0\leq \vout/\kms\leq 50$.  
We find three important consequences of rotation.
First, it increases the detected flux at the line's center in comparison with the
non-rotational case, second it produces a line broadening and third it introduces
a dependency with the  viewing angle.
We also develp a semi-analytic model that modifies the spectra of
pure outflow simulations that manages to reproduce the main features of the
Monte Carlo simulations.
As an application to observational data we constraint the rotation
parameters of a set of observed LAE emission spectra.    
\end{abstract}

@@

Figure \ref{fig:standard_deviation} summarizes the STD results for all
our models.
Each panel shows the STD as a function of \vrot.
The black triangles correspond to the full RT solution and the line to
the Doppler Shift approximation. 
The optical depth increases from top to bottom and the outflow
velocity from left to right.
This quantitative plot confirms that the line width increases with
rotational velocity, all else being equal.
The Doppler Shift sucessfuly reproduces this trend, albeit a consistent
underestimation of the RT values; this underestimation has as an upper
bound of $\sim 7\%$, $3\%$ and $\sim 2\%$ for $\tauh=10^5$, $10^6$ and
$10^7$, respectively.
Tee Doppler Shift approximation also improves as the outflow velocity
decreases.
